\documentclass[10pt,a4paper]{article}

% ---- packages (all standard; compiles on Overleaf and Tectonic) ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}

\definecolor{accent}{HTML}{1F4E79}
\definecolor{muted}{HTML}{555555}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

% tighten everything
\setlength{\parindent}{0pt}
\pagestyle{empty}
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=2pt, parsep=0pt}

% ---- section styling -----------------------------------------------------
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\vspace{-0.6em}\color{accent}\rule{\linewidth}{0.8pt}]
\titlespacing{\section}{0pt}{8pt}{4pt}

% ---- helpers -------------------------------------------------------------
% entry: {title}{date}{subtitle}{place}
\newcommand{\entry}[4]{%
  \textbf{#1}\hfill{\color{muted}\small #2}\\[1pt]
  {\color{accent}\itshape #3}\hfill{\color{muted}\itshape\small #4}\par\vspace{2pt}}

\newcommand{\headerrule}{\vspace{2pt}\hrule\vspace{6pt}}

\begin{document}

% ====================== HEADER ============================================
\begin{center}
  {\Huge\bfseries\color{accent} MD Minhazur Rahman}\\[3pt]
  {\large Data Scientist \textperiodcentered\ Machine Learning Engineer}\\[5pt]
  {\small\color{muted}
    Chittagong, Bangladesh (open to relocation / visa sponsorship) \quad
    \href{mailto:minhazurrahman.ds@gmail.com}{minhazurrahman.ds@gmail.com} \quad
    +880 1303 454309}\\[3pt]
  {\small
    \href{https://github.com/minhazda}{github.com/minhazda} \quad
    \href{https://www.linkedin.com/in/mohammadminhaz/}{in/mohammadminhaz} \quad
    \href{https://orcid.org/0009-0008-9418-6614}{ORCID 0009-0008-9418-6614}}
\end{center}

% ====================== SUMMARY ===========================================
\section{Summary}
Data scientist and ML engineer with an MSc in Data Science (University of Greenwich) and 3+ years of
industry data and IT experience. I ship production-grade machine learning end to end --- forecasting,
imbalanced classification, streaming, and LLM/RAG --- with two models live on GCP Cloud Run (Terraform,
keyless CI/CD, monitoring), a Kafka stream scorer proven end-to-end on Kubernetes in CI, and an
orchestrated weekly-retraining platform (Dagster, dbt). First-author DOI-indexed preprint. Open to
Data Scientist / ML Engineer roles worldwide with relocation and visa sponsorship.

% ====================== PROJECTS ==========================================
\section{Selected Projects \textnormal{\small (all public; two live)}}

\entry{Real-Time Demand Forecasting --- Production MLOps Pipeline}{2026}{LightGBM \textperiodcentered\ FastAPI \textperiodcentered\ Docker \textperiodcentered\ Terraform \textperiodcentered\ Cloud Run}{\href{https://github.com/minhazda/synthetic-retail-mlops-pipeline}{github.com/minhazda/synthetic-retail-mlops-pipeline}}
\begin{itemize}
  \item \textbf{Cut forecast error 40.8\% MAE / 47.3\% RMSE vs.\ a seasonal-naive baseline} by building a typed, tested LightGBM pipeline with a single shared feature module that eliminates training/serving skew.
  \item \textbf{Deployed a live, public inference API on GCP Cloud Run} provisioned entirely as code (Terraform) with keyless GitHub$\rightarrow$GCP CI/CD (Workload Identity Federation --- no stored secrets).
  \item \textbf{Added production observability} with Prometheus metrics, a Grafana dashboard, and Evidently data-drift reporting on the running service.
\end{itemize}

\entry{Real-Time Card-Fraud Detection --- Imbalanced Classification}{2026}{LightGBM \textperiodcentered\ scikit-learn \textperiodcentered\ FastAPI \textperiodcentered\ Docker \textperiodcentered\ Terraform \textperiodcentered\ Cloud Run}{\href{https://github.com/minhazda/fraud-detection-mlops}{github.com/minhazda/fraud-detection-mlops}}
\begin{itemize}
  \item \textbf{Reached ROC-AUC 0.90 and PR-AUC 0.49 ($\sim$8$\times$ the base rate) on held-out data} by handling class imbalance (\texttt{scale\_pos\_weight}) and tuning the decision threshold on a separate validation split.
  \item \textbf{Served real-time scoring with built-in explainability} --- engineering features from raw transactions at request time and surfacing the risk signals behind each decision in an interactive demo UI.
\end{itemize}

\entry{Event-Driven Fraud Scoring --- Kafka Stream Processing}{2026}{Kafka/Redpanda \textperiodcentered\ Kubernetes \textperiodcentered\ pydantic \textperiodcentered\ Prometheus}{\href{https://github.com/minhazda/streaming-fraud-detection}{github.com/minhazda/streaming-fraud-detection}}
\begin{itemize}
  \item \textbf{Built a real-time Kafka/Redpanda stream processor} scoring raw transactions with the fraud model: strict schema validation into a dead-letter queue, an alerts topic, and Prometheus scoring-latency histograms --- with zero training/serving skew (a unit test pins stream scores to batch predictions at $10^{-9}$).
  \item \textbf{Proved the stack on Kubernetes in CI:} the pipeline unit-tests without a broker via a \texttt{MessageBus} protocol, then every push runs it end-to-end against a real Redpanda broker and deploys it onto a kind cluster.
\end{itemize}

\entry{Orchestrated Retraining Platform --- Champion/Challenger}{2026}{Dagster \textperiodcentered\ dbt \textperiodcentered\ DuckDB \textperiodcentered\ LightGBM \textperiodcentered\ GitHub Actions}{\href{https://github.com/minhazda/retail-demand-platform}{github.com/minhazda/retail-demand-platform}}
\begin{itemize}
  \item \textbf{Orchestrated the full data-to-model graph as Dagster assets:} dbt builds a tested star schema on DuckDB (data-quality tests run as a pipeline stage), then a LightGBM challenger retrains weekly on 1M+ real retail transactions via a scheduled CI job.
  \item \textbf{Gated deployment on evidence, not retraining:} a champion/challenger rule promotes a new model only on a $\geq$1\% holdout-MAE improvement, with champion metrics versioned in git.
  \item \textbf{Proved the feature logic scales past one machine:} a PySpark twin of the feature frame (window API), parity-tested against the pandas implementation to $10^{-9}$ in CI on a real JVM.
\end{itemize}

\entry{Demand Forecasting on Real Retail Data (UCI Online Retail II)}{2026}{pandas \textperiodcentered\ LightGBM \textperiodcentered\ DuckDB \textperiodcentered\ time-series}{\href{https://github.com/minhazda/real-retail-forecasting}{github.com/minhazda/real-retail-forecasting}}
\begin{itemize}
  \item \textbf{Improved pooled MAE 26.3\% over a seasonal-naive baseline (beating it on 47/49 product series)} by documenting defensible cleaning of 1.07M real transactions and reproducing the findings in DuckDB SQL.
\end{itemize}

\entry{Privacy-Preserving RAG Agent --- LLM Tool-Calling}{2026}{LangGraph \textperiodcentered\ ChromaDB \textperiodcentered\ on-device embeddings \textperiodcentered\ FastAPI}{\href{https://github.com/minhazda/privacy-preserving-rag-agent}{github.com/minhazda/privacy-preserving-rag-agent}}
\begin{itemize}
  \item \textbf{Shipped a tool-calling RAG agent behind a fail-closed privacy guard} (on-device embeddings, PII redaction) and built a two-tier evaluation: a deterministic CI gate plus a Claude LLM-as-judge harness with Langfuse tracing.
\end{itemize}

\entry{A/B Experiment Analysis Toolkit}{2026}{statistics \textperiodcentered\ CUPED \textperiodcentered\ sequential testing \textperiodcentered\ Hypothesis}{\href{https://github.com/minhazda/experiment-analysis-toolkit}{github.com/minhazda/experiment-analysis-toolkit}}
\begin{itemize}
  \item \textbf{Built a typed experimentation toolkit} (power analysis, CUPED variance reduction, always-valid sequential testing) whose test suite verifies the \emph{statistical guarantees themselves}: family-wise false-positive rate under continuous peeking and CI coverage over simulation.
\end{itemize}

% ====================== EXPERIENCE ========================================
\section{Professional Experience}

\entry{GPH Ispat Limited}{Feb 2022 -- Aug 2024}{Officer --- Information Technology Department}{Chittagong, Bangladesh}
\begin{itemize}
  \item \textbf{Automated departmental reporting and operational workflows} by developing internal Python and SQL tools, reducing manual effort across materials-management and reporting processes.
  \item \textbf{Sustained daily operational continuity for enterprise systems} used across departments at one of Bangladesh's largest publicly listed (DSE) steel manufacturers, through proactive maintenance and troubleshooting.
  \item \textbf{Safeguarded data integrity across inventory tracking} by monitoring and reviewing materials-management data feeding company reporting.
\end{itemize}

\entry{Vcube Soft \& Tech}{2021 -- Feb 2022}{QA Engineer --- Computer Vision Data}{Chittagong, Bangladesh}
\begin{itemize}
  \item \textbf{Raised training-data quality for production 3D floor-plan reconstruction models} by curating and validating annotated 360\textdegree\ image datasets and enforcing metadata consistency.
  \item \textbf{Built QA validation pipelines} that systematically caught annotation errors before they reached model training.
\end{itemize}

% ====================== EDUCATION =========================================
\section{Education}

\entry{MSc Data Science --- Pass with Merit}{Sep 2024 -- Jan 2026}{University of Greenwich}{London, United Kingdom}
\begin{itemize}
  \item Dissertation (70\%): real-time retail demand forecasting on privacy-preserving synthetic data --- 37\% MAE reduction; published as a first-author DOI-indexed preprint (Zenodo).
  \item Modules: Applied Machine Learning 71\%, Cloud Computing \& HPC 74\%, Big Data Analytics, Statistical Methods for Time Series.
\end{itemize}

\entry{BSc Computer Science \& Engineering}{Jan 2017 -- Jan 2021}{Independent University, Chittagong}{Chittagong, Bangladesh}
\begin{itemize}
  \item Final-year project: rare-event detection in surveillance video using 3D-ResNet18 and a custom CNN (PyTorch) on the UCF Crime dataset.
\end{itemize}

% ====================== SKILLS ============================================
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
  \textbf{\color{accent}Languages} & Python, SQL, C++, R \\[2pt]
  \textbf{\color{accent}ML / DS} & scikit-learn, LightGBM, XGBoost, Random Forest, PyTorch; time-series forecasting, imbalanced classification, feature engineering \\[2pt]
  \textbf{\color{accent}MLOps / Cloud} & Docker, Kubernetes, Terraform (IaC), GCP Cloud Run, GitHub Actions (CI/CD), MLflow, Prometheus, Grafana, Evidently \\[2pt]
  \textbf{\color{accent}Streaming / Pipelines} & Kafka (Redpanda), PySpark, Dagster, dbt, DuckDB; schema validation, dead-letter queues, champion/challenger promotion \\[2pt]
  \textbf{\color{accent}LLM / GenAI} & LangGraph, RAG, ChromaDB, LLM-as-judge evaluation, Langfuse \\[2pt]
  \textbf{\color{accent}Serving / Data} & FastAPI, pandas, NumPy, SQL; rolling-origin cross-validation, model evaluation \\[2pt]
  \textbf{\color{accent}Testing / Quality} & pytest, Hypothesis (property-based), mypy, ruff; typed, tested, reproducible repos \\
\end{tabularx}

% ====================== EXTRAS ============================================
\section{Publications, Awards \& Research}
\begin{itemize}
  \item \textbf{Publication:} Rahman, M.\,M. (2026). ``Synthetic Retail Time-Series for Privacy-Preserving Demand Forecasting.'' Preprint, Zenodo. DOI: \href{https://doi.org/10.5281/zenodo.19479285}{10.5281/zenodo.19479285}.
  \item \textbf{HPC research:} parallel 2D Jacobi solver in C++/OpenMP on an Azure HPC cluster --- 4.81$\times$ speedup on 8 threads.
  \item \textbf{Awards:} Winner, Game of Presentations 2019 (inter-university); Second Runner-Up, City Bank Bankers' Hunt 2020 (national case competition).
  \item \textbf{Teaching:} supplementary ML instruction to 10+ MSc peers; 4 years of independent STEM/Python tutoring (15+ students).
\end{itemize}

% ====================== REFERENCE =========================================
\section{Reference}
Dr.\ Tuan Vuong --- MSc Dissertation Supervisor, University of Greenwich \textperiodcentered\ \href{mailto:T.Vuong@greenwich.ac.uk}{T.Vuong@greenwich.ac.uk}. Further references available on request.

\end{document}
